Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
minor fix in intro

There are two basic ways to represent cast efficiently: coercions 
\citep{herman2010space}\citep{siek2009exploring}\citep{siek2012interpretations} 
\citep{siek2015blame} and threesomes 
\citep{siek2010threesomes}\citep{garcia2013calculating}. They have different 
strength and 
weakness. \citet{garcia2013calculating} and \citet{siek2015blame} claim that 
coercion is easy to understand, but hard to implement, while threesome is easy 
to implement, but hard to understand. \citet{garcia2013calculating} in addition 
claims that coercion is more difficult to reason about formally, because 
composition of coercions is not structurally recurisive. The developers of 
Grift \citep{kuhlenschmidt2018efficient} affirm that it is tricky to convince 
their proof assistants that composition of coercions terminates.

We present a new cast representation, hypercoercion, which has a structurally 
recursive composition. We believe hypercoercion is easier to understand than 
threesome, because its syntax is close to coercion. For instance, the 
coercion approach represents $ 
\cOOcast{\TOOdyn}{l}{\cOOcast{\POOunit}{l'}{\TOOdyn}} $ as $ \POOunit 
?^{l} ; \POOunit\! $, while the hypercoercion approach gives $ 
\hyperCoercionC{?^l}{\POOunit}{!} $. In Section~\ref{sec:background}, we review 
coercion together with cast calculus, the intermediate languages in 
\citet{kuhlenschmidt2018efficient}. And we present hypercoerion in 
Section~\ref{sec:hypercoercion-definition}.

@@

Some readers might know that there are four blame strategies: $ \{Lazy, Eager\} 
\times \{D, UD\} $. Eager strategies detect more potential type errors, but 
blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. 
\todo[inline]{Why do we need to explain why both LD and LUD? -KC}

@@

$ T_1 \sim T_2 $ reads ``$ T_1 $ and $ T_2 $ are consistent''.
The intuition of $ T_1 \sim T $ is that $ T_1 $ and $ T_2 $ have no conflict 
type information. Two types are consistent if one of them is $ \star $, or they 
have the same top-most type constructor and the corresponding sub-parts are 
consistent. Consistency is reflexive and symmetric, but not transitive.

>>>>

There are two basic ways to represent cast space-efficiently: coercions 
\citep{herman2010space}\citep{siek2009exploring}\citep{siek2012interpretations} 
\citep{siek2015blame} and threesomes 
\citep{siek2010threesomes}\citep{garcia2013calculating}. They have different 
strength and 
weakness. \citet{garcia2013calculating} and \citet{siek2015blame} claim that 
coercion is easy to understand, but hard to implement, while threesome is easy 
to implement, but hard to understand. \citet{garcia2013calculating} in addition 
claims that coercion is more difficult to reason about formally because 
its compose function is not structurally recurisive. For instance, the 
developers of Grift \citep{kuhlenschmidt2018efficient} report that it is tricky 
to convince their proof assistants that the compose function terminates.

We present a new cast representation, hypercoercion, which has a structurally 
recursive composition. When we prove theorems about hypercoercion in Agda, the 
definition ``just works''. 
Besides, We believe hypercoercion is about as easy to understand as coercion 
because their syntax definitions are similar. For instance, the 
coercion approach represents $ 
\cOOcast{\TOOdyn}{l}{\cOOcast{\POOunit}{l'}{\TOOdyn}} $ as $ \POOunit 
?^{l} ; \POOunit\! $, while the hypercoercion approach gives $ 
\hyperCoercionC{?^l}{\POOunit}{!} $. In Section~\ref{sec:background}, we review 
coercion together with cast calculus, an intermediate languages for gradual 
typing \citep{siek2009exploring}\citep{kuhlenschmidt2018efficient}. And we 
present hypercoerion in Section~\ref{sec:hypercoercion-definition}.

@@

Some readers might know that there are four blame strategies: $ \{Lazy, Eager\} 
\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
potential type errors, but 
blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. 
\todo[inline]{Why do we need to explain why both LD and LUD? -KC}

@@

$ T_1 \sim T_2 $ reads ``$ T_1 $ and $ T_2 $ are consistent''.
The intuition of $ T_1 \sim T_2 $ is that $ T_1 $ and $ T_2 $ have no conflict 
type information. Two types are consistent if one of them is $ \star $, or they 
have the same top-most type constructor and the corresponding sub-parts are 
consistent. Consistency is reflexive and symmetric, but not transitive.
